How to Name a Real-World Object, and how not

### 2019-12-06 papers/ACL2020/acl2020_main.tex
add crowdsource task screenshot back in

%\appendix
%
%\section{Appendices}
%\label{sec:appendix}
%Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
%Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
%Upon acceptance, the appendices come after the references, as shown here.
%
%\paragraph{\LaTeX-specific details:}
%Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
%
%
%\section{Supplemental Material}
%\label{sec:supplemental}
%Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
%Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

>>>>

%\appendix
%
\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{images/verification-interface.pdf}
  \caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
  \label{fig:verification-interface}
\end{figure*}
